---
title: "Various Simulations to Compare Cox Regression and Logistic Regression - Exponential"
author: "Rebecca Irlmeier<br><small>Department of Biostatistics<br>Vanderbilt University School of Medicine</small>"
date: "<small>`r Sys.Date()`</small>"
output:
  html_document:
    toc: no
    toc_depth: 3
    number_sections: false
    toc_float: 
      collapsed: false
    code_folding: hide
    theme: cosmo
description: "Various Simulations"
---

```{r warning = FALSE, message = FALSE}
library(Rlab)
library(survival)
library(survminer)
library(knitr)
library(actuar)
library(logistf)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(splines)
library(grDevices)
```

## Simulations

There are two different simulations that are explored in this report.

1. The delayed error time is added to the event time only, and the observed time with error is the minimum of the true event time plus error and the true censoring time: $\tilde{T}_{obs}=min(T_e+\epsilon,T_c)$
2. The delayed error time is added to both $T_e$ and $T_c$ to obtain the observed time with error: $\bar{T}_{obs}=min(T_e-\epsilon, T_c-\epsilon)$

## Error Scenarios

There are five different error scenarios that are generated in this simulation, which can be specified by the input variable *error*:

* error = 0 or error = "none": there is no error term
* error = 1 or error = "ind" : error term is independent of the covariates
* error = 2 or error = "z" : error term depends on the binary exposure $z$
* error = 3 or error = "x1" : error term depends on the binary covariate $x_1$ (confounder)
* error = 4 or error = "x2" : error term depends on the continuous covariate $x_2$

## Results {.tabset .tabset-fade}

### Simulation 1 - Exponential, large

**Functions**

* The event time is simulated from an Exponential distribution
* The parameters lead to a large number of observations in Error Case 2

```{r functions-1, warning = FALSE, message = FALSE}
# Generate data
survdata <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda) {
  set.seed(seed) # Set seed
  
  x1 <- rbern(n, p1) # Generate x1 (confounder)
  x2 <- rnorm(n, mu, sd) # Generate x2
  z <- rbern(n, 1/(1 + exp(-alpha_vec[1] - alpha_vec[2]*x1))) # Generate z (exposure)
  
  # Generate error term for five scenarios
    # No error
  if (error == 0 | error == "none") {
    error_time <- rep(0, n)
    # Error independent
  } else if (error == 1 | error == "ind") {
    error_time <- runif(n, min = 20, max = 800)
    # Error depends on z
  } else if (error == 2 | error == "z") {
    error_time <- ifelse(z == 1, runif(n, min = 60, max = 100), runif(n, min = 100, max = 1400))
    # Error depends on x1 (confounder)
  } else if (error == 3 | error == "x1") {
    error_time <- ifelse(x1 == 1, runif(n, min = 60, max = 100), runif(n, min = 100, max = 1400))
    # Error depends on x2
  } else if (error == 4 | error == "x2") {
    error_time <- rlnorm(n, meanlog = 10*x2, sdlog = 1)
    # Invalid input
  } else {
    print("Invalid input for err")
  }
    
  time_event_pre <- (-log(runif(n, min = 0, max = 1)))*exp(-beta_1*z - beta_vec[1]*x1 - beta_vec[2]*x2)/lambda # Simulated event time from Cox-Exp
  time_error_pre <- time_event_pre + error_time # Add simulated error time to original time
  time_censor <- runif(n, min = 430, max = 500) # Censoring time
  
  data <- data.frame(cbind(x1, x2, z, time_event_pre, time_error_pre, time_censor))  
  
  data$event <- ifelse(data$time_event_pre <= data$time_censor, 1, 0) # Event indicator for original time
  data$time_event <- ifelse(data$event == 1, data$time_event_pre, data$time_censor) # Actual time with event
  data$event_error <- ifelse(data$time_error_pre <= data$time_censor, 1, 0) # Event indicator for original + error time
  data$time_error <- ifelse(data$event_error == 1, data$time_error_pre, data$time_censor) # Actual time with event + error
  
  # Get data from the different scenarios of error
  error_case1 <- data %>% filter(event_error == 0) %>% filter(time_censor < time_event_pre)
  error_case2 <- data %>% filter(event_error == 0) %>% filter(time_event_pre < time_censor & time_censor < time_error_pre)
  error_case3 <- data %>% filter(event_error == 1) %>% filter(time_censor > time_error_pre)
  
  data.list <- list(data, error_case1, error_case2, error_case3)
  return(data.list)
}

# Fit Coxph and logistic models on data
models <- function(data.list){
  data <- data.list[[1]]
  # Coxph model
  m1 <- coxph(Surv(time_error, event_error) ~ z + x1 + x2, data = data) # Fit cox model
  a <- summary(m1) # Model summary
  
  reject1 <- ifelse(a$coefficients["z", "Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  beta_est <- a$coefficients["z","coef"] # Beta estimate for z
  CI_lw <- log(a$conf.int["z", "lower .95"]) # Lower bound of CI for beta for z
  CI_up <- log(a$conf.int["z", "upper .95"]) # Upper bound of CI for beta for z

  # logistic model adjusting for time
  m2 <- glm(event_error ~ z + x1 + x2 + ns(time_error, df=3), data = data, family = binomial()) # Fit logistic model
  b <- summary(m2) # Model summary
  reject2 <- ifelse(b$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  # logistic model without time
  m3 <- glm(event_error ~ z + x1 + x2, data = data, family = binomial()) # Fit logistic model
  c <- summary(m3) # Model summary
  reject3 <- ifelse(c$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  # logistic model adjusting for record length
  m4 <- glm(event_error ~ z + x1 + x2 + ns(time_censor, df=3), data = data, family = binomial()) # Fit logistic model
  d <- summary(m4) # Model summary
  reject4 <- ifelse(d$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  event_rate <- sum(data$event)/dim(data)[1] # Event rate
  mean_z <- mean(data$z) # Mean exposure
  result <- c(mean_z, event_rate, beta_est, CI_lw, CI_up, reject1, reject2, reject3, reject4) # Results
  return(result)
}

# Loop
meanloop <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda, loopnum) {
  results_all <- matrix(NA, loopnum, 9) # Initialize 
  # Generate data and store results loopnum times
  for (i in 1:loopnum) {
    data.list <- survdata(seed + i, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda)
    results_all[i, ] <- models(data.list)
  }
  return(results_all)
}

# Output
output <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda, loopnum) {
  result <- matrix(NA, 0, 9)
  for (i in seq_along(beta_1)) {
    output <- meanloop(seed=seed, n=n, error=error, p1=p1, mu=mu, sd=sd, alpha_vec=alpha_vec, beta_1=beta_1[i],
                       beta_vec=beta_vec, lambda=lambda, loopnum=loopnum)
    result <- rbind(result,
                    c(mean(output[,1]), # Mean exposure rate
                      mean(output[,2]), # Mean event rate
                      mean(output[,3])-beta_1[i], # Bias
                      sd(output[,3]), # SD
                      mean((output[,3]-beta_1[i])^2), # MSE
                      sum(output[,6])/loopnum, # Type 1 error Cox/Power Cox
                      sum(output[,7])/loopnum, # Type 1 error logistic (with time)/Power logistic (with time)
                      sum(output[,8])/loopnum, # Type 1 error logistic (without time)/Power logistic (without time)
                      sum(output[,9])/loopnum)) # Type 1 error logistic (with record length)/Power logistic (with record length)
  }
  colnames(result) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
  rownames(result) <- c("beta = 0", "beta = log(1.1)", "beta = log(1.15)", "beta = log(1.25)", "beta = log(1.5)", "beta = log(2)")
  return(result)
}
```

**No error**
```{r error0-1, warning = FALSE, message = FALSE}
# Results
result0 <- read.csv('result01.csv', row.names=1)
colnames(result0) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result0, digits = 4, main = "No Error")
```

```{r res_fig0-1}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result0[, "Type I Cox/Power Cox"]
log_time <- result0[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result0[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result0[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res0_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="No Error", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23), legend.title = element_text(size=25), legend.text = element_text(size=25), legend.key.size = unit(4,"line")) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
leg <- get_legend(res0_fig)
res0_fig_nl <- res0_fig + theme(legend.position = "none")
  
res0_fig_tab <- ggarrange(res0_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

**Error term is independent of the covariates**
```{r error1-1, warning = FALSE, message = FALSE}
# Results
result1 <- read.csv('result11.csv', row.names=1)
colnames(result1) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result1, digits = 4, main = "Error Independent")
```

```{r res_fig1-1}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result1[, "Type I Cox/Power Cox"]
log_time <- result1[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result1[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result1[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res1_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="Error Independent", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res1_fig_nl <- res1_fig + theme(legend.position = "none")
  
res1_fig_tab <- ggarrange(res1_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

```{r warning = FALSE, message = FALSE}
data <- survdata(seed=123, n=500, error=1, p1=0.3, mu=0.5, sd=0.4, alpha_vec=c(-1.25,1), beta_1=log(2), beta_vec=c(log(2),log(2)), lambda=0.001)

n <- c(dim(data[[1]])[1], dim(data[[2]])[1], dim(data[[3]])[1], dim(data[[4]])[1])
title <- c(paste0("Complete Data, N = ", n[1]), paste0("Delayed Event Time Case 1, n = ", n[2]), paste0("Delayed Event Time Case 2, n = ", n[3]), paste0("Delayed Event Time Case 3, n = ", n[4]))

hist_comp <- ggplot(data[[1]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[1], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_1 <- ggplot(data[[2]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[2], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_2 <- ggplot(data[[3]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[3], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_3 <- ggplot(data[[4]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[4], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#jpeg("hist_sim1_exp_sz.jpeg", units="in", width=5, height=4, res=300)
ggarrange(hist_comp, hist_1, hist_2, hist_3, common.legend = TRUE, legend="bottom")
#dev.off()
```

**Error term depends on the binary exposure $z$**
```{r error2-1, warning = FALSE, message = FALSE}
# Results
result2 <- read.csv('result21.csv', row.names=1)
colnames(result2) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result2, digits = 4, main = "Error Dependent on $z$ (Exposure)", escape=FALSE)
```

```{r res_fig2-1}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result2[, "Type I Cox/Power Cox"]
log_time <- result2[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result2[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result2[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res2_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="Error Dependent on Exposure, z", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res2_fig_nl <- res2_fig + theme(legend.position = "none")
  
res2_fig_tab <- ggarrange(res2_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

```{r warning = FALSE, message = FALSE}
data <- survdata(seed=123, n=500, error=2, p1=0.3, mu=0.5, sd=0.4, alpha_vec=c(-1.25,1), beta_1=log(2), beta_vec=c(log(2),log(2)), lambda=0.001)

n <- c(dim(data[[1]])[1], dim(data[[2]])[1], dim(data[[3]])[1], dim(data[[4]])[1])
title <- c(paste0("Complete Data, N = ", n[1]), paste0("Delayed Event Time Case 1, n = ", n[2]), paste0("Delayed Event Time Case 2, n = ", n[3]), paste0("Delayed Event Time Case 3, n = ", n[4]))

hist_comp <- ggplot(data[[1]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[1], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_1 <- ggplot(data[[2]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[2], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_2 <- ggplot(data[[3]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[3], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_3 <- ggplot(data[[4]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[4], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#jpeg("hist_sim1_exp_l_z.jpeg", units="in", width=7, height=6, res=300)
ggarrange(hist_comp, hist_1, hist_2, hist_3, common.legend = TRUE, legend="bottom")
#dev.off()
```

**Error term depends on the binary covariate $x_1$ (confounder)**
```{r error3-1, warning = FALSE, message = FALSE}
# Results
result3 <- read.csv('result31.csv', row.names=1)
colnames(result3) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result3, digits = 4, main = "Error Dependent on $x_1$ (Confounder)", escape=FALSE)
```

```{r res_fig3-1}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result3[, "Type I Cox/Power Cox"]
log_time <- result3[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result3[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result3[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res3_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title=expression(paste("Error Dependent on Confounder, ", x[1])), color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res3_fig_nl <- res3_fig + theme(legend.position = "none")
  
res3_fig_tab <- ggarrange(res3_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

```{r warning = FALSE, message = FALSE}
data <- survdata(seed=123, n=500, error=3, p1=0.3, mu=0.5, sd=0.4, alpha_vec=c(-1.25,1), beta_1=log(2), beta_vec=c(log(2),log(2)), lambda=0.001)

n <- c(dim(data[[1]])[1], dim(data[[2]])[1], dim(data[[3]])[1], dim(data[[4]])[1])
title <- c(paste0("Complete Data, N = ", n[1]), paste0("Error Case 1, n = ", n[2]), paste0("Error Case 2, n = ", n[3]), paste0("Error Case 3, n = ", n[4]))

hist_comp <- ggplot(data[[1]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[1], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_1 <- ggplot(data[[2]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[2], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_2 <- ggplot(data[[3]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[3], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_3 <- ggplot(data[[4]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[4], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#jpeg("hist_sim1_exp_sz.jpeg", units="in", width=5, height=4, res=300)
ggarrange(hist_comp, hist_1, hist_2, hist_3, common.legend = TRUE, legend="bottom")
#dev.off()
```

**Error term depends on the continuous covariate $x_2$**
```{r error4-1, warning = FALSE, message = FALSE}
# Results
result4 <- read.csv('result41.csv', row.names=1)
colnames(result4) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result4, digits = 4, main = "Error Dependent on $x_2$", escape=FALSE)
```

```{r res_fig4-1}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result4[, "Type I Cox/Power Cox"]
log_time <- result4[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result4[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result4[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res4_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title=expression(paste("Error Dependent on ", x[2])), color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res4_fig_nl <- res4_fig + theme(legend.position = "none")
  
res4_fig_tab <- ggarrange(res4_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

```{r warning = FALSE, message = FALSE}
data <- survdata(seed=123, n=500, error=4, p1=0.3, mu=0.5, sd=0.4, alpha_vec=c(-1.25,1), beta_1=log(2), beta_vec=c(log(2),log(2)), lambda=0.001)

n <- c(dim(data[[1]])[1], dim(data[[2]])[1], dim(data[[3]])[1], dim(data[[4]])[1])
title <- c(paste0("Complete Data, N = ", n[1]), paste0("Error Case 1, n = ", n[2]), paste0("Error Case 2, n = ", n[3]), paste0("Error Case 3, n = ", n[4]))

hist_comp <- ggplot(data[[1]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[1], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_1 <- ggplot(data[[2]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[2], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_2 <- ggplot(data[[3]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[3], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_3 <- ggplot(data[[4]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[4], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#jpeg("hist_sim1_exp_sz.jpeg", units="in", width=5, height=4, res=300)
ggarrange(hist_comp, hist_1, hist_2, hist_3, common.legend = TRUE, legend="bottom")
#dev.off()
```

```{r res_fig1, fig.width=24, fig.height=18}
#jpeg("res_sim1_exp_l.jpeg", units="in", width=24, height=18, res=300)
# leg <- get_legend(res_fig0)
# res_fig0 <- res_fig0 + theme(legend.position = "none")
# res_fig1 <- res_fig1 + theme(legend.position = "none")
# res_fig2 <- res_fig2 + theme(legend.position = "none")
# res_fig3 <- res_fig3 + theme(legend.position = "none")
# res_fig4 <- res_fig4 + theme(legend.position = "none")
ggarrange(res0_fig_tab, res1_fig_tab, res2_fig_tab, res3_fig_tab, res4_fig_tab, leg, nrow=2, ncol=3)
#dev.off()
```

```{r}
res_fig <- function(result0, result1, result2, result3, result4) {
  betas <- rep(c(1, 1.1, 1.15, 1.25, 1.5, 2), 4*5)
  #betas <- rep(c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"), 4*5)
  #betas <- factor(betas, levels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
  cox <- c(result0[, "Type I Cox/Power Cox"], result1[, "Type I Cox/Power Cox"], result2[, "Type I Cox/Power Cox"], result3[, "Type I Cox/Power Cox"], result4[, "Type I Cox/Power Cox"])
  lrm_obs <- c(result0[, "Type I logistic (with time)/Power logistic (with time)"], result1[, "Type I logistic (with time)/Power logistic (with time)"], result2[, "Type I logistic (with time)/Power logistic (with time)"], result3[, "Type I logistic (with time)/Power logistic (with time)"], result4[, "Type I logistic (with time)/Power logistic (with time)"])
  lrm_u <- c(result0[, "Type I logistic (without time)/Power logistic (without time)"], result1[, "Type I logistic (without time)/Power logistic (without time)"], result2[, "Type I logistic (without time)/Power logistic (without time)"], result3[, "Type I logistic (without time)/Power logistic (without time)"], result4[, "Type I logistic (without time)/Power logistic (without time)"])
  lrm_rl <- c(result0[, "Type I logistic (with record length)/Power logistic (with record length)"], result1[, "Type I logistic (with record length)/Power logistic (with record length)"], result2[, "Type I logistic (with record length)/Power logistic (with record length)"], result3[, "Type I logistic (with record length)/Power logistic (with record length)"], result4[, "Type I logistic (with record length)/Power logistic (with record length)"])
  eval <- c(cox, lrm_obs, lrm_u, lrm_rl)
  lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
  lb <- ifelse(lb < 0, 0, lb)
  ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
  ub <- ifelse(ub > 1, 1, ub)
  Model <- c(rep("Cox", 6*5), rep("LRMobs", 6*5), rep("LRMu", 6*5), rep("LRMrl", 6*5))
  Model <- factor(Model, levels=c("Cox", "LRMobs", "LRMu", "LRMrl"))
  #det <- rep(c(rep("No delayed event time", 6), rep("Independent", 6), rep("Exposure", 6), rep("Confounder", 6), rep("Covariate", 6)), 4)
  det <- rep(c(rep("Delayed event time: none", 6), rep("Delayed event time: independent", 6), rep("Delayed event time: exposure", 6), rep("Delayed event time: confounder", 6), rep("Delayed event time: covariate", 6)), 4)
  #det <- factor(det, levels=c("No delayed event time", "Delayed event time is independent", "Delayed event time depends on exposure", "Delayed event time depends on confounder", "Delayed event time depends on covariate")) 
  det <- factor(det, levels=c("Delayed event time: none", "Delayed event time: independent", "Delayed event time: exposure", "Delayed event time: confounder", "Delayed event time: covariate")) 
  res_df <- data.frame(betas, eval, lb, ub, Model, det)

  ggplot(res_df, aes(x=betas, y=eval, col=Model, group=Model)) +
    geom_line() + geom_point(size=0.7) +
    geom_errorbar(aes(ymin=lb, ymax=ub, width=0.035)) +
    geom_hline(yintercept=0.05, linetype="dashed", color="black") +
    facet_wrap(~ det) +
    ylim(0,1) +
    labs(x="Hazard Ratio for Exposure, z", y="Type I Error and Power *") + 
    theme_bw() + 
    theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=35, vjust=0.8, hjust=0.7, size=7), axis.text.y = element_text(size=9), axis.title.x = element_text(size=12), axis.title.y = element_text(size=12), title = element_text(size=23), legend.position=c(0.85, 0.18), legend.title = element_text(size=12), strip.text = element_text(size=11)) + scale_x_continuous(breaks=c(1, 1.1, 1.15, 1.25, 1.5, 2), labels=c("1", "1.1", "1.15", "1.25", "1.5", "2"))
}
```

```{r fig.width=9, fig.height=6}
#tiff("res_sim1_exp_l.tiff", units="in", width=9, height=6, res=300)
#jpeg("res_sim1_exp_l.jpeg", units="in", width=9, height=6, res=300)
res_fig(result0, result1, result2, result3, result4)
#dev.off()
```

```{r fig.width=7, fig.height=4, warning=FALSE, message=FALSE, eval=FALSE}
# Bias graph
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 5)
bias <- c(result0[, "Bias"], result1[, "Bias"], result2[, "Bias"], result3[, "Bias"], result4[, "Bias"])
sd_bias <- c(result0[, "SD"], result1[, "SD"], result2[, "SD"], result3[, "SD"], result4[, "SD"])
error <- factor(c(rep("None", 6), rep("Independent", 6), rep("Exposure", 6), rep("Confounder", 6), rep("Covariate", 6)), levels=c("None", "Independent", "Exposure", "Confounder", "Covariate"))
lb <- bias - qnorm(0.975)*sd_bias/sqrt(5000)
ub <- bias + qnorm(0.975)*sd_bias/sqrt(5000)
bias_df <- data.frame(betas, bias, error, lb, ub)

bias_tab_df <- data.frame(rbind(t(round(bias[1:6],4)), t(round(bias[7:12],4)), t(round(bias[13:18],4)), t(round(bias[19:24],4)), t(round(bias[25:30],4))))
rownames(bias_tab_df) <- c("None", "Independent", "Exposure", "Confounder", "Covariate")
colnames(bias_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
bias_tab <- tableGrob(bias_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#E76BF3", "#00B0F6","#00BF7D", "#F8766D", "#A3A500"))), rowhead=list(fg_params=list(fontface="plain")), base_size=10))

bias_fig <- ggplot(bias_df, aes(x=betas, y=bias, col=error)) + geom_point(position=position_dodge(0.04)) + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.1), position=position_dodge(0.04)) + geom_hline(yintercept=0, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Bias", title="Bias of Beta Coefficient for Exposure, z, from Model 1 (Cox)", color="Error") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))

bias_fig_nl <- bias_fig + theme(legend.position = "none")
bias_fig_tab <- ggarrange(bias_fig_nl, bias_tab, nrow=2, heights=c(2,1)) 

#jpeg("bias_sim1_exp_l.jpeg", units="in", width=7, height=4, res=300)
bias_fig
#dev.off()
```

```{r}
result0_exp_l <- result0
result1_exp_l <- result1
result2_exp_l <- result2
result3_exp_l <- result3
result4_exp_l <- result4
```


### Simulation 1 - Exponential, small

**Functions**

* The event time is simulated from an Exponential distribution
* The parameters lead to a small number of observations in Error Case 2

```{r functions-2, warning = FALSE, message = FALSE}
# Generate data
survdata <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda) {
  set.seed(seed) # Set seed
  
  x1 <- rbern(n, p1) # Generate x1 (confounder)
  x2 <- rnorm(n, mu, sd) # Generate x2
  z <- rbern(n, 1/(1 + exp(-alpha_vec[1] - alpha_vec[2]*x1))) # Generate z (exposure)
  
  # Generate error term for five scenarios
    # No error
  if (error == 0 | error == "none") {
    error_time <- rep(0, n)
    # Error independent
  } else if (error == 1 | error == "ind") {
    error_time <- runif(n, min = 20, max = 40)
    # Error depends on z
  } else if (error == 2 | error == "z") {
    error_time <- ifelse(z == 1, runif(n, min = 20, max = 40), runif(n, min = 40, max = 60))
    # Error depends on x1 (confounder)
  } else if (error == 3 | error == "x1") {
    error_time <- ifelse(x1 == 1, runif(n, min = 20, max = 40), runif(n, min = 40, max = 60))
    # Error depends on x2
  } else if (error == 4 | error == "x2") {
    error_time <- rlnorm(n, meanlog = 5*x2, sdlog = 1)
    # Invalid input
  } else {
    print("Invalid input for err")
  }
    
  time_event_pre <- (-log(runif(n, min = 0, max = 1)))*exp(-beta_1*z - beta_vec[1]*x1 - beta_vec[2]*x2)/lambda # Simulated event time from Cox-Exp
  time_error_pre <- time_event_pre + error_time # Add simulated error time to original time
  time_censor <- runif(n, min = 160, max = 260) # Censoring time
  
  data <- data.frame(cbind(x1, x2, z, time_event_pre, time_error_pre, time_censor))  
  
  data$event <- ifelse(data$time_event_pre <= data$time_censor, 1, 0) # Event indicator for original time
  data$time_event <- ifelse(data$event == 1, data$time_event_pre, data$time_censor) # Actual time with event
  data$event_error <- ifelse(data$time_error_pre <= data$time_censor, 1, 0) # Event indicator for original + error time
  data$time_error <- ifelse(data$event_error == 1, data$time_error_pre, data$time_censor) # Actual time with event + error
  
  # Get data from the different scenarios of error
  error_case1 <- data %>% filter(event_error == 0) %>% filter(time_censor < time_event_pre)
  error_case2 <- data %>% filter(event_error == 0) %>% filter(time_event_pre < time_censor & time_censor < time_error_pre)
  error_case3 <- data %>% filter(event_error == 1) %>% filter(time_censor > time_error_pre)
  
  data.list <- list(data, error_case1, error_case2, error_case3)
  return(data.list)
}

# Fit Coxph and logistic models on data
models <- function(data.list){
  data <- data.list[[1]]
  # Coxph model
  m1 <- coxph(Surv(time_error, event_error) ~ z + x1 + x2, data = data) # Fit cox model
  a <- summary(m1) # Model summary
  
  reject1 <- ifelse(a$coefficients["z", "Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  beta_est <- a$coefficients["z","coef"] # Beta estimate for z
  CI_lw <- log(a$conf.int["z", "lower .95"]) # Lower bound of CI for beta for z
  CI_up <- log(a$conf.int["z", "upper .95"]) # Upper bound of CI for beta for z

  # logistic model adjusting for time
  m2 <- glm(event_error ~ z + x1 + x2 + ns(time_error, df=3), data = data, family = binomial()) # Fit logistic model
  b <- summary(m2) # Model summary
  reject2 <- ifelse(b$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  # logistic model without time
  m3 <- glm(event_error ~ z + x1 + x2, data = data, family = binomial()) # Fit logistic model
  c <- summary(m3) # Model summary
  reject3 <- ifelse(c$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  # logistic model adjusting for record length
  m4 <- glm(event_error ~ z + x1 + x2 + ns(time_censor, df=3), data = data, family = binomial()) # Fit logistic model
  d <- summary(m4) # Model summary
  reject4 <- ifelse(d$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  event_rate <- sum(data$event)/dim(data)[1] # Event rate
  mean_z <- mean(data$z) # Mean exposure
  result <- c(mean_z, event_rate, beta_est, CI_lw, CI_up, reject1, reject2, reject3, reject4) # Results
  return(result)
}

# Loop
meanloop <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda, loopnum) {
  results_all <- matrix(NA, loopnum, 9) # Initialize 
  # Generate data and store results loopnum times
  for (i in 1:loopnum) {
    data.list <- survdata(seed + i, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda)
    results_all[i, ] <- models(data.list)
  }
  return(results_all)
}

# Output
output <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda, loopnum) {
  result <- matrix(NA, 0, 9)
  for (i in seq_along(beta_1)) {
    output <- meanloop(seed=seed, n=n, error=error, p1=p1, mu=mu, sd=sd, alpha_vec=alpha_vec, beta_1=beta_1[i],
                       beta_vec=beta_vec, lambda=lambda, loopnum=loopnum)
    result <- rbind(result,
                    c(mean(output[,1]), # Mean exposure rate
                      mean(output[,2]), # Mean event rate
                      mean(output[,3])-beta_1[i], # Bias
                      sd(output[,3]), # SD
                      mean((output[,3]-beta_1[i])^2), # MSE
                      sum(output[,6])/loopnum, # Type 1 error Cox/Power Cox
                      sum(output[,7])/loopnum, # Type 1 error logistic (with time)/Power logistic (with time)
                      sum(output[,8])/loopnum, # Type 1 error logistic (without time)/Power logistic (without time)
                      sum(output[,9])/loopnum)) # Type 1 error logistic (with record length)/Power logistic (with record length)
  }
  colnames(result) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
  rownames(result) <- c("beta = 0", "beta = log(1.1)", "beta = log(1.15)", "beta = log(1.25)", "beta = log(1.5)", "beta = log(2)")
  return(result)
}
```

**No error**
```{r error0-2, warning = FALSE, message = FALSE}
# Results
result0 <- read.csv('result02.csv', row.names=1)
colnames(result0) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result0, digits = 4, main = "No Error")
```

```{r res_fig0-2}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result0[, "Type I Cox/Power Cox"]
log_time <- result0[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result0[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result0[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res0_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="No Error", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23), legend.title = element_text(size=25), legend.text = element_text(size=25), legend.key.size = unit(4,"line")) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
leg <- get_legend(res0_fig)
res0_fig_nl <- res0_fig + theme(legend.position = "none")
  
res0_fig_tab <- ggarrange(res0_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

**Error term is independent of the covariates**
```{r error1-2, warning = FALSE, message = FALSE}
# Results
result1 <- read.csv('result12.csv', row.names=1)
colnames(result1) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result1, digits = 4, main = "Error Independent")
```

```{r res_fig1-2}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result1[, "Type I Cox/Power Cox"]
log_time <- result1[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result1[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result1[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res1_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="Error Independent", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res1_fig_nl <- res1_fig + theme(legend.position = "none")
  
res1_fig_tab <- ggarrange(res1_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

```{r warning = FALSE, message = FALSE}
data <- survdata(seed=123, n=500, error=1, p1=0.3, mu=0.5, sd=0.4, alpha_vec=c(-1.25,1), beta_1=log(2), beta_vec=c(log(2),log(2)), lambda=0.001)

n <- c(dim(data[[1]])[1], dim(data[[2]])[1], dim(data[[3]])[1], dim(data[[4]])[1])
title <- c(paste0("Complete Data, N = ", n[1]), paste0("Error Case 1, n = ", n[2]), paste0("Error Case 2, n = ", n[3]), paste0("Error Case 3, n = ", n[4]))

hist_comp <- ggplot(data[[1]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[1], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_1 <- ggplot(data[[2]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[2], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_2 <- ggplot(data[[3]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[3], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_3 <- ggplot(data[[4]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[4], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#jpeg("hist_sim1_exp_sz.jpeg", units="in", width=5, height=4, res=300)
ggarrange(hist_comp, hist_1, hist_2, hist_3, common.legend = TRUE, legend="bottom")
#dev.off()
```

**Error term depends on the binary exposure $z$**
```{r error2-2, warning = FALSE, message = FALSE}
# Results
result2 <- read.csv('result22.csv', row.names=1)
colnames(result2) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result2, digits = 4, main = "Error Dependent on $z$ (Exposure)", escape=FALSE)
```

```{r res_fig2-2}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result2[, "Type I Cox/Power Cox"]
log_time <- result2[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result2[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result2[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res2_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="Error Dependent on Exposure, z", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res2_fig_nl <- res2_fig + theme(legend.position = "none")
  
res2_fig_tab <- ggarrange(res2_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

```{r warning = FALSE, message = FALSE}
data <- survdata(seed=123, n=500, error=2, p1=0.3, mu=0.5, sd=0.4, alpha_vec=c(-1.25,1), beta_1=log(2), beta_vec=c(log(2),log(2)), lambda=0.001)

n <- c(dim(data[[1]])[1], dim(data[[2]])[1], dim(data[[3]])[1], dim(data[[4]])[1])
title <- c(paste0("Complete Data, N = ", n[1]), paste0("Delayed Event Time Case 1, n = ", n[2]), paste0("Delayed Event Time Case 2, n = ", n[3]), paste0("Delayed Event Time Case 3, n = ", n[4]))

hist_comp <- ggplot(data[[1]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[1], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_1 <- ggplot(data[[2]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[2], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_2 <- ggplot(data[[3]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[3], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_3 <- ggplot(data[[4]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[4], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#jpeg("hist_sim1_exp_s_z.jpeg", units="in", width=7, height=6, res=300)
ggarrange(hist_comp, hist_1, hist_2, hist_3, common.legend = TRUE, legend="bottom")
#dev.off()
```

**Error term depends on the binary covariate $x_1$ (confounder)**
```{r error3-2, warning = FALSE, message = FALSE}
# Results
result3 <- read.csv('result32.csv', row.names=1)
colnames(result3) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result3, digits = 4, main = "Error Dependent on $x_1$ (Confounder)", escape=FALSE)
```

```{r res_fig3-2}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result3[, "Type I Cox/Power Cox"]
log_time <- result3[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result3[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result3[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res3_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title=expression(paste("Error Dependent on Confounder, ", x[1])), color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res3_fig_nl <- res3_fig + theme(legend.position = "none")
  
res3_fig_tab <- ggarrange(res3_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

```{r warning = FALSE, message = FALSE}
data <- survdata(seed=123, n=500, error=3, p1=0.3, mu=0.5, sd=0.4, alpha_vec=c(-1.25,1), beta_1=log(2), beta_vec=c(log(2),log(2)), lambda=0.001)

n <- c(dim(data[[1]])[1], dim(data[[2]])[1], dim(data[[3]])[1], dim(data[[4]])[1])
title <- c(paste0("Complete Data, N = ", n[1]), paste0("Error Case 1, n = ", n[2]), paste0("Error Case 2, n = ", n[3]), paste0("Error Case 3, n = ", n[4]))

hist_comp <- ggplot(data[[1]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[1], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_1 <- ggplot(data[[2]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[2], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_2 <- ggplot(data[[3]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[3], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_3 <- ggplot(data[[4]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[4], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#jpeg("hist_sim1_exp_sz.jpeg", units="in", width=5, height=4, res=300)
ggarrange(hist_comp, hist_1, hist_2, hist_3, common.legend = TRUE, legend="bottom")
#dev.off()
```

**Error term depends on the continuous covariate $x_2$**
```{r error4-2, warning = FALSE, message = FALSE}
# Results
result4 <- read.csv('result42.csv', row.names=1)
colnames(result4) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result4, digits = 4, main = "Error Dependent on $x_2$", escape=FALSE)
```

```{r res_fig4-2}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result4[, "Type I Cox/Power Cox"]
log_time <- result4[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result4[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result4[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res4_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title=expression(paste("Error Dependent on ", x[2])), color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res4_fig_nl <- res4_fig + theme(legend.position = "none")
  
res4_fig_tab <- ggarrange(res4_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

```{r warning = FALSE, message = FALSE}
data <- survdata(seed=123, n=500, error=4, p1=0.3, mu=0.5, sd=0.4, alpha_vec=c(-1.25,1), beta_1=log(2), beta_vec=c(log(2),log(2)), lambda=0.001)

n <- c(dim(data[[1]])[1], dim(data[[2]])[1], dim(data[[3]])[1], dim(data[[4]])[1])
title <- c(paste0("Complete Data, N = ", n[1]), paste0("Error Case 1, n = ", n[2]), paste0("Error Case 2, n = ", n[3]), paste0("Error Case 3, n = ", n[4]))

hist_comp <- ggplot(data[[1]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[1], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_1 <- ggplot(data[[2]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[2], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_2 <- ggplot(data[[3]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[3], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
hist_3 <- ggplot(data[[4]]) + geom_histogram(aes(time_event, fill="True Time"), alpha=0.7) + geom_histogram(aes(time_error, fill="Error Time"), alpha=0.7) + xlim(0,500) + labs(title=title[4], x="Time", y="Frequency", fill="Legend") + scale_color_manual(values=colors) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#jpeg("hist_sim1_exp_sz.jpeg", units="in", width=5, height=4, res=300)
ggarrange(hist_comp, hist_1, hist_2, hist_3, common.legend = TRUE, legend="bottom")
#dev.off()
```

```{r res_fig2, fig.width=24, fig.height=18}
#jpeg("res_sim1_exp_s.jpeg", units="in", width=24, height=18, res=300)
# leg <- get_legend(res_fig0)
# res_fig0 <- res_fig0 + theme(legend.position = "none")
# res_fig1 <- res_fig1 + theme(legend.position = "none")
# res_fig2 <- res_fig2 + theme(legend.position = "none")
# res_fig3 <- res_fig3 + theme(legend.position = "none")
# res_fig4 <- res_fig4 + theme(legend.position = "none")
ggarrange(res0_fig_tab, res1_fig_tab, res2_fig_tab, res3_fig_tab, res4_fig_tab, leg, nrow=2, ncol=3)
#dev.off()
```

```{r fig.width=9, fig.height=6}
#tiff("res_sim1_exp_s.tiff", units="in", width=9, height=6, res=300)
#jpeg("res_sim1_exp_s.jpeg", units="in", width=9, height=6, res=300)
res_fig(result0, result1, result2, result3, result4)
#dev.off()
```

```{r fig.width=7, fig.height=4, warning=FALSE, message=FALSE, eval=FALSE}
# Bias graph
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 5)
bias <- c(result0[, "Bias"], result1[, "Bias"], result2[, "Bias"], result3[, "Bias"], result4[, "Bias"])
sd_bias <- c(result0[, "SD"], result1[, "SD"], result2[, "SD"], result3[, "SD"], result4[, "SD"])
error <- factor(c(rep("None", 6), rep("Independent", 6), rep("Exposure", 6), rep("Confounder", 6), rep("Covariate", 6)), levels=c("None", "Independent", "Exposure", "Confounder", "Covariate"))
lb <- bias - qnorm(0.975)*sd_bias/sqrt(5000)
ub <- bias + qnorm(0.975)*sd_bias/sqrt(5000)
bias_df <- data.frame(betas, bias, error, lb, ub)

bias_tab_df <- data.frame(rbind(t(round(bias[1:6],4)), t(round(bias[7:12],4)), t(round(bias[13:18],4)), t(round(bias[19:24],4)), t(round(bias[25:30],4))))
rownames(bias_tab_df) <- c("None", "Independent", "Exposure", "Confounder", "Covariate")
colnames(bias_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
bias_tab <- tableGrob(bias_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#E76BF3", "#00B0F6","#00BF7D", "#F8766D", "#A3A500"))), rowhead=list(fg_params=list(fontface="plain")), base_size=10))

bias_fig <- ggplot(bias_df, aes(x=betas, y=bias, col=error)) + geom_point(position=position_dodge(0.04)) + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03), position=position_dodge(0.04)) + geom_hline(yintercept=0, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Bias", title="Bias of Beta Coefficient for Exposure, z, from Model 1 (Cox)", color="Error") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))

bias_fig_nl <- bias_fig + theme(legend.position = "none")
bias_fig_tab <- ggarrange(bias_fig_nl, bias_tab, nrow=2, heights=c(2,1)) 

#jpeg("bias_sim1_exp_s.jpeg", units="in", width=7, height=4, res=300)
bias_fig
#dev.off()
```

```{r}
result0_exp_s <- result0
result1_exp_s <- result1
result2_exp_s <- result2
result3_exp_s <- result3
result4_exp_s <- result4
```


### Simulation 2 - Exponential, large

**Functions**

* The event time is simulated from an Exponential distribution
* The parameters lead to a large number of observations in Error Case 2

```{r functions-3, warning = FALSE, message = FALSE}
# Generate data
survdata <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda) {
  set.seed(seed) # Set seed
  
  x1 <- rbern(n, p1) # Generate x1 (confounder)
  x2 <- rnorm(n, mu, sd) # Generate x2
  z <- rbern(n, 1/(1 + exp(-alpha_vec[1] - alpha_vec[2]*x1))) # Generate z (exposure)
  
  # Generate error term for five scenarios
    # No error
  if (error == 0 | error == "none") {
    error_time <- rep(0, n)
    # Error independent
  } else if (error == 1 | error == "ind") {
    error_time <- runif(n, min = 20, max = 800)
    # Error depends on z
  } else if (error == 2 | error == "z") {
    error_time <- ifelse(z == 1, runif(n, min = 60, max = 100), runif(n, min = 100, max = 1400))
    # Error depends on x1 (confounder)
  } else if (error == 3 | error == "x1") {
    error_time <- ifelse(x1 == 1, runif(n, min = 60, max = 100), runif(n, min = 100, max = 1400))
    # Error depends on x2
  } else if (error == 4 | error == "x2") {
    error_time <- rlnorm(n, meanlog = 10*x2, sdlog = 1)
    # Invalid input
  } else {
    print("Invalid input for err")
  }
    
  time_event_pre <- (-log(runif(n, min = 0, max = 1)))*exp(-beta_1*z - beta_vec[1]*x1 - beta_vec[2]*x2)/lambda # Simulated event time from Cox-Exp
  time_event_error <- time_event_pre - error_time # Event time + error
  time_censor <- runif(n, min = 430, max = 500) # Censoring time
  time_censor_error <- time_censor - error_time # Censoring time + error
  
  data <- data.frame(cbind(x1, x2, z, time_event_pre, time_censor, time_event_error, time_censor_error))  
  data <- data %>% filter(time_event_error > 0 & time_censor_error > 0)
  
  data$event <- ifelse(data$time_event_pre <= data$time_censor, 1, 0) # Event indicator for original time
  data$time_event <- ifelse(data$event == 1, data$time_event_pre, data$time_censor) # Actual time with event
  data$event_error <- ifelse(data$time_event_error <= data$time_censor_error, 1, 0) # Event indicator for original + error time
  data$time_error <- ifelse(data$event_error == 1, data$time_event_error, data$time_censor_error) # Actual time with event + error
  
  return(data)
}

# Fit Coxph and logistic models on data
models <- function(data){
  # Coxph model
  m1 <- coxph(Surv(time_error, event_error) ~ z + x1 + x2, data = data) # Fit cox model
  a <- summary(m1) # Model summary
  
  reject1 <- ifelse(a$coefficients["z", "Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  beta_est <- a$coefficients["z","coef"] # Beta estimate for z
  CI_lw <- log(a$conf.int["z", "lower .95"]) # Lower bound of CI for beta for z
  CI_up <- log(a$conf.int["z", "upper .95"]) # Upper bound of CI for beta for z

  # logistic model adjusting for time
  m2 <- glm(event_error ~ z + x1 + x2 + ns(time_error, df=3), data = data, family = binomial()) # Fit logistic model
  b <- summary(m2) # Model summary
  reject2 <- ifelse(b$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  # logistic model without time
  m3 <- glm(event_error ~ z + x1 + x2, data = data, family = binomial()) # Fit logistic model
  c <- summary(m3) # Model summary
  reject3 <- ifelse(c$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  # logistic model adjusting for record length
  m4 <- glm(event_error ~ z + x1 + x2 + ns(time_censor_error, df=3), data = data, family = binomial()) # Fit logistic model
  d <- summary(m4) # Model summary
  reject4 <- ifelse(d$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  event_rate <- sum(data$event)/dim(data)[1] # Event rate
  mean_z <- mean(data$z) # Mean exposure
  result <- c(mean_z, event_rate, beta_est, CI_lw, CI_up, reject1, reject2, reject3, reject4) # Results
  return(result)
}

# Loop
meanloop <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda, loopnum) {
  results_all <- matrix(NA, loopnum, 9) # Initialize 
  # Generate data and store results loopnum times
  for (i in 1:loopnum) {
    data.list <- survdata(seed + i, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda)
    results_all[i, ] <- models(data.list)
  }
  return(results_all)
}

# Output
output <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda, loopnum) {
  result <- matrix(NA, 0, 9)
  for (i in seq_along(beta_1)) {
    output <- meanloop(seed=seed, n=n, error=error, p1=p1, mu=mu, sd=sd, alpha_vec=alpha_vec, beta_1=beta_1[i],
                       beta_vec=beta_vec, lambda=lambda, loopnum=loopnum)
    result <- rbind(result,
                    c(mean(output[,1]), # Mean exposure rate
                      mean(output[,2]), # Mean event rate
                      mean(output[,3])-beta_1[i], # Bias
                      sd(output[,3]), # SD
                      mean((output[,3]-beta_1[i])^2), # MSE
                      sum(output[,6])/loopnum, # Type 1 error Cox/Power Cox
                      sum(output[,7])/loopnum, # Type 1 error logistic (with time)/Power logistic (with time)
                      sum(output[,8])/loopnum, # Type 1 error logistic (without time)/Power logistic (without time)
                      sum(output[,9])/loopnum)) # Type 1 error logistic (with record length)/Power logistic (with record length)
  }
  colnames(result) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
  rownames(result) <- c("beta = 0", "beta = log(1.1)", "beta = log(1.15)", "beta = log(1.25)", "beta = log(1.5)", "beta = log(2)")
  return(result)
}
```

**No error**
```{r error0-3, warning = FALSE, message = FALSE}
# Results
result0 <- read.csv('result03.csv', row.names=1)
colnames(result0) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result0, digits = 4, main = "No Error")
```

```{r res_fig0-3}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result0[, "Type I Cox/Power Cox"]
log_time <- result0[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result0[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result0[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res0_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="No Error", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23), legend.title = element_text(size=25), legend.text = element_text(size=25), legend.key.size = unit(4,"line")) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
leg <- get_legend(res0_fig)
res0_fig_nl <- res0_fig + theme(legend.position = "none")
  
res0_fig_tab <- ggarrange(res0_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

**Error term is independent of the covariates**
```{r error1-3, warning = FALSE, message = FALSE}
# Results
result1 <- read.csv('result13.csv', row.names=1)
colnames(result1) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result1, digits = 4, main = "Error Independent")
```

```{r res_fig1-3}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result1[, "Type I Cox/Power Cox"]
log_time <- result1[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result1[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result1[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res1_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="Error Independent", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res1_fig_nl <- res1_fig + theme(legend.position = "none")
  
res1_fig_tab <- ggarrange(res1_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

**Error term depends on the binary exposure $z$**
```{r error2-3, warning = FALSE, message = FALSE}
# Results
result2 <- read.csv('result23.csv', row.names=1)
colnames(result2) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result2, digits = 4, main = "Error Dependent on $z$ (Exposure)", escape=FALSE)
```

```{r res_fig2-3}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result2[, "Type I Cox/Power Cox"]
log_time <- result2[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result2[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result2[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res2_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="Error Dependent on Exposure, z", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res2_fig_nl <- res2_fig + theme(legend.position = "none")
  
res2_fig_tab <- ggarrange(res2_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

**Error term depends on the binary covariate $x_1$ (confounder)**
```{r error3-3, warning = FALSE, message = FALSE}
# Results
result3 <- read.csv('result33.csv', row.names=1)
colnames(result3) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result3, digits = 4, main = "Error Dependent on $x_1$ (Confounder)", escape=FALSE)
```

```{r res_fig3-3}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result3[, "Type I Cox/Power Cox"]
log_time <- result3[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result3[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result3[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res3_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title=expression(paste("Error Dependent on Confounder, ", x[1])), color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res3_fig_nl <- res3_fig + theme(legend.position = "none")
  
res3_fig_tab <- ggarrange(res3_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

**Error term depends on the continuous covariate $x_2$**
```{r error4-3, warning = FALSE, message = FALSE}
# Results
result4 <- read.csv('result43.csv', row.names=1)
colnames(result4) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result4, digits = 4, main = "Error Dependent on $x_2$", escape=FALSE)
```

```{r res_fig4-3}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result4[, "Type I Cox/Power Cox"]
log_time <- result4[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result4[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result4[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res4_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title=expression(paste("Error Dependent on ", x[2])), color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res4_fig_nl <- res4_fig + theme(legend.position = "none")
  
res4_fig_tab <- ggarrange(res4_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

```{r res_fig3, fig.width=24, fig.height=18}
#jpeg("res_sim2_exp_l.jpeg", units="in", width=24, height=18, res=300)
# leg <- get_legend(res_fig0)
# res_fig0 <- res_fig0 + theme(legend.position = "none")
# res_fig1 <- res_fig1 + theme(legend.position = "none")
# res_fig2 <- res_fig2 + theme(legend.position = "none")
# res_fig3 <- res_fig3 + theme(legend.position = "none")
# res_fig4 <- res_fig4 + theme(legend.position = "none")
ggarrange(res0_fig_tab, res1_fig_tab, res2_fig_tab, res3_fig_tab, res4_fig_tab, leg, nrow=2, ncol=3)
#dev.off()
```

```{r fig.width=9, fig.height=6}
#tiff("res_sim2_exp_l.tiff", units="in", width=9, height=6, res=300)
#jpeg("res_sim2_exp_l.jpeg", units="in", width=9, height=6, res=300)
res_fig(result0, result1, result2, result3, result4)
#dev.off()
```

```{r fig.width=7, fig.height=4, warning=FALSE, message=FALSE, eval=FALSE}
# Bias graph
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 5)
bias <- c(result0[, "Bias"], result1[, "Bias"], result2[, "Bias"], result3[, "Bias"], result4[, "Bias"])
sd_bias <- c(result0[, "SD"], result1[, "SD"], result2[, "SD"], result3[, "SD"], result4[, "SD"])
error <- factor(c(rep("None", 6), rep("Independent", 6), rep("Exposure", 6), rep("Confounder", 6), rep("Covariate", 6)), levels=c("None", "Independent", "Exposure", "Confounder", "Covariate"))
lb <- bias - qnorm(0.975)*sd_bias/sqrt(5000)
ub <- bias + qnorm(0.975)*sd_bias/sqrt(5000)
bias_df <- data.frame(betas, bias, error, lb, ub)

bias_tab_df <- data.frame(rbind(t(round(bias[1:6],4)), t(round(bias[7:12],4)), t(round(bias[13:18],4)), t(round(bias[19:24],4)), t(round(bias[25:30],4))))
rownames(bias_tab_df) <- c("None", "Independent", "Exposure", "Confounder", "Covariate")
colnames(bias_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
bias_tab <- tableGrob(bias_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#E76BF3", "#00B0F6","#00BF7D", "#F8766D", "#A3A500"))), rowhead=list(fg_params=list(fontface="plain")), base_size=10))

bias_fig <- ggplot(bias_df, aes(x=betas, y=bias, col=error)) + geom_point(position=position_dodge(0.04)) + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03), position=position_dodge(0.04)) + geom_hline(yintercept=0, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Bias", title="Bias of Beta Coefficient for Exposure, z, from Model 1 (Cox)", color="Error") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))

bias_fig_nl <- bias_fig + theme(legend.position = "none")
bias_fig_tab <- ggarrange(bias_fig_nl, bias_tab, nrow=2, heights=c(2,1)) 

#jpeg("bias_sim2_exp_l.jpeg", units="in", width=7, height=4, res=300)
bias_fig
#dev.off()
```

```{r}
result0_exp_l_sim2 <- result0
result1_exp_l_sim2 <- result1
result2_exp_l_sim2 <- result2
result3_exp_l_sim2 <- result3
result4_exp_l_sim2 <- result4
```


### Simulation 2 - Exponential, small

**Functions**

* The event time is simulated from an Exponential distribution
* The parameters lead to a small number of observations in Error Case 2

```{r functions-4, warning = FALSE, message = FALSE}
# Generate data
survdata <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda) {
  set.seed(seed) # Set seed
  
  x1 <- rbern(n, p1) # Generate x1 (confounder)
  x2 <- rnorm(n, mu, sd) # Generate x2
  z <- rbern(n, 1/(1 + exp(-alpha_vec[1] - alpha_vec[2]*x1))) # Generate z (exposure)
  
  # Generate error term for five scenarios
    # No error
  if (error == 0 | error == "none") {
    error_time <- rep(0, n)
    # Error independent
  } else if (error == 1 | error == "ind") {
    error_time <- runif(n, min = 20, max = 40)
    # Error depends on z
  } else if (error == 2 | error == "z") {
    error_time <- ifelse(z == 1, runif(n, min = 20, max = 40), runif(n, min = 40, max = 60))
    # Error depends on x1 (confounder)
  } else if (error == 3 | error == "x1") {
    error_time <- ifelse(x1 == 1, runif(n, min = 20, max = 40), runif(n, min = 40, max = 60))
    # Error depends on x2
  } else if (error == 4 | error == "x2") {
    error_time <- rlnorm(n, meanlog = 5*x2, sdlog = 1)
    # Invalid input
  } else {
    print("Invalid input for err")
  }
    
  time_event_pre <- (-log(runif(n, min = 0, max = 1)))*exp(-beta_1*z - beta_vec[1]*x1 - beta_vec[2]*x2)/lambda # Simulated event time from Cox-Exp
  time_event_error <- time_event_pre - error_time # Event time + error
  time_censor <- runif(n, min = 160, max = 260) # Censoring time
  time_censor_error <- time_censor - error_time # Censoring time + error
  
  data <- data.frame(cbind(x1, x2, z, time_event_pre, time_censor, time_event_error, time_censor_error))  
  data <- data %>% filter(time_event_error > 0 & time_censor_error > 0)
  
  data$event <- ifelse(data$time_event_pre <= data$time_censor, 1, 0) # Event indicator for original time
  data$time_event <- ifelse(data$event == 1, data$time_event_pre, data$time_censor) # Actual time with event
  data$event_error <- ifelse(data$time_event_error <= data$time_censor_error, 1, 0) # Event indicator for original + error time
  data$time_error <- ifelse(data$event_error == 1, data$time_event_error, data$time_censor_error) # Actual time with event + error
  
  return(data)
}

# Fit Coxph and logistic models on data
models <- function(data){
  # Coxph model
  m1 <- coxph(Surv(time_error, event_error) ~ z + x1 + x2, data = data) # Fit cox model
  a <- summary(m1) # Model summary
  
  reject1 <- ifelse(a$coefficients["z", "Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  beta_est <- a$coefficients["z","coef"] # Beta estimate for z
  CI_lw <- log(a$conf.int["z", "lower .95"]) # Lower bound of CI for beta for z
  CI_up <- log(a$conf.int["z", "upper .95"]) # Upper bound of CI for beta for z

  # logistic model adjusting for time
  m2 <- glm(event_error ~ z + x1 + x2 + ns(time_error, df=3), data = data, family = binomial()) # Fit logistic model
  b <- summary(m2) # Model summary
  reject2 <- ifelse(b$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  # logistic model without time
  m3 <- glm(event_error ~ z + x1 + x2, data = data, family = binomial()) # Fit logistic model
  c <- summary(m3) # Model summary
  reject3 <- ifelse(c$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  # logistic model adjusting for record length
  m4 <- glm(event_error ~ z + x1 + x2 + ns(time_censor_error, df=3), data = data, family = binomial()) # Fit logistic model
  d <- summary(m4) # Model summary
  reject4 <- ifelse(d$coefficients["z","Pr(>|z|)"] < 0.05, 1, 0) # Reject p-value
  
  event_rate <- sum(data$event)/dim(data)[1] # Event rate
  mean_z <- mean(data$z) # Mean exposure
  result <- c(mean_z, event_rate, beta_est, CI_lw, CI_up, reject1, reject2, reject3, reject4) # Results
  return(result)
}

# Loop
meanloop <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda, loopnum) {
  results_all <- matrix(NA, loopnum, 9) # Initialize 
  # Generate data and store results loopnum times
  for (i in 1:loopnum) {
    data.list <- survdata(seed + i, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda)
    results_all[i, ] <- models(data.list)
  }
  return(results_all)
}

# Output
output <- function(seed, n, error, p1, mu, sd, alpha_vec, beta_1, beta_vec, lambda, loopnum) {
  result <- matrix(NA, 0, 9)
  for (i in seq_along(beta_1)) {
    output <- meanloop(seed=seed, n=n, error=error, p1=p1, mu=mu, sd=sd, alpha_vec=alpha_vec, beta_1=beta_1[i],
                       beta_vec=beta_vec, lambda=lambda, loopnum=loopnum)
    result <- rbind(result,
                    c(mean(output[,1]), # Mean exposure rate
                      mean(output[,2]), # Mean event rate
                      mean(output[,3])-beta_1[i], # Bias
                      sd(output[,3]), # SD
                      mean((output[,3]-beta_1[i])^2), # MSE
                      sum(output[,6])/loopnum, # Type 1 error Cox/Power Cox
                      sum(output[,7])/loopnum, # Type 1 error logistic (with time)/Power logistic (with time)
                      sum(output[,8])/loopnum, # Type 1 error logistic (without time)/Power logistic (without time)
                      sum(output[,9])/loopnum)) # Type 1 error logistic (with record length)/Power logistic (with record length)
  }
  colnames(result) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
  rownames(result) <- c("beta = 0", "beta = log(1.1)", "beta = log(1.15)", "beta = log(1.25)", "beta = log(1.5)", "beta = log(2)")
  return(result)
}
```

**No error**
```{r error0-4, warning = FALSE, message = FALSE}
# Results
result0 <- read.csv('result04.csv', row.names=1)
colnames(result0) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result0, digits = 4, main = "No Error")
```

```{r res_fig0-4}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result0[, "Type I Cox/Power Cox"]
log_time <- result0[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result0[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result0[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res0_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="No Error", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23), legend.title = element_text(size=25), legend.text = element_text(size=25), legend.key.size = unit(4,"line")) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
leg <- get_legend(res0_fig)
res0_fig_nl <- res0_fig + theme(legend.position = "none")
  
res0_fig_tab <- ggarrange(res0_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

**Error term is independent of the covariates**
```{r error1-4, warning = FALSE, message = FALSE}
# Results
result1 <- read.csv('result14.csv', row.names=1)
colnames(result1) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result1, digits = 4, main = "Error Independent")
```

```{r res_fig1-4}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result1[, "Type I Cox/Power Cox"]
log_time <- result1[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result1[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result1[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res1_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="Error Independent", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res1_fig_nl <- res1_fig + theme(legend.position = "none")
  
res1_fig_tab <- ggarrange(res1_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

**Error term depends on the binary exposure $z$**
```{r error2-4, warning = FALSE, message = FALSE}
# Results
result2 <- read.csv('result24.csv', row.names=1)
colnames(result2) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result2, digits = 4, main = "Error Dependent on $z$ (Exposure)", escape=FALSE)
```

```{r res_fig2-4}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result2[, "Type I Cox/Power Cox"]
log_time <- result2[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result2[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result2[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res2_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title="Error Dependent on Exposure, z", color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res2_fig_nl <- res2_fig + theme(legend.position = "none")
  
res2_fig_tab <- ggarrange(res2_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

**Error term depends on the binary covariate $x_1$ (confounder)**
```{r error3-4, warning = FALSE, message = FALSE}
# Results
result3 <- read.csv('result34.csv', row.names=1)
colnames(result3) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result3, digits = 4, main = "Error Dependent on $x_1$ (Confounder)", escape=FALSE)
```

```{r res_fig3-4}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result3[, "Type I Cox/Power Cox"]
log_time <- result3[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result3[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result3[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))

res3_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title=expression(paste("Error Dependent on Confounder, ", x[1])), color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res3_fig_nl <- res3_fig + theme(legend.position = "none")
  
res3_fig_tab <- ggarrange(res3_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

**Error term depends on the continuous covariate $x_2$**
```{r error4-4, warning = FALSE, message = FALSE}
# Results
result4 <- read.csv('result44.csv', row.names=1)
colnames(result4) <- c("Mean Exposure Rate", "Mean Event Rate", "Bias", "SD", "MSE", "Type I Cox/Power Cox", "Type I logistic (with time)/Power logistic (with time)", "Type I logistic (without time)/Power logistic (without time)", "Type I logistic (with record length)/Power logistic (with record length)")
kable(result4, digits = 4, main = "Error Dependent on $x_2$", escape=FALSE)
```

```{r res_fig4-4}
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 4)
cox <- result4[, "Type I Cox/Power Cox"]
log_time <- result4[, "Type I logistic (with time)/Power logistic (with time)"]
log_wotime <- result4[, "Type I logistic (without time)/Power logistic (without time)"]
log_reclen <- result4[, "Type I logistic (with record length)/Power logistic (with record length)"]
eval <- c(cox, log_time, log_wotime, log_reclen)
lb <- eval - qnorm(0.975)*sqrt((eval*(1-eval))/5000)
lb <- ifelse(lb < 0, 0, lb)
ub <- eval + qnorm(0.975)*sqrt((eval*(1-eval))/5000)
ub <- ifelse(ub > 1, 1, ub)
mod <- c(rep("Cox", 6), rep("LRM1", 6), rep("LRM2", 6), rep("LRM3", 6))
mod <- factor(mod, levels=c("Cox", "LRM1", "LRM2", "LRM3"))
res_df <- data.frame(betas, eval, lb, ub, mod)

res_tab_df <- data.frame(rbind(t(round(eval[1:6],3)), t(round(eval[7:12],3)), t(round(eval[13:18],3)), t(round(eval[19:24],3))))
rownames(res_tab_df) <- c("Cox", "LRM1", "LRM2", "LRM3")
colnames(res_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
res_tab <- tableGrob(res_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#F8766D", "#7CAE00","#00BFC4", "#C77CFF"))), rowhead=list(fg_params=list(fontface="plain")), base_size=19))
res4_fig <- ggplot(res_df, aes(x=betas, y=eval, col=mod)) + geom_line() + geom_point() + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03)) + geom_hline(yintercept=0.05, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Type I Error/Power", title=expression(paste("Error Dependent on ", x[2])), color="Model") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72, size=15), axis.text.y = element_text(size=15), axis.title.x = element_text(size=20), axis.title.y = element_text(size=20), title = element_text(size=23)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))
res4_fig_nl <- res4_fig + theme(legend.position = "none")
  
res4_fig_tab <- ggarrange(res4_fig_nl, res_tab, nrow=2, heights=c(2.4,1)) 
```

```{r res_fig4, fig.width=24, fig.height=18}
#jpeg("res_sim2_exp_s.jpeg", units="in", width=24, height=18, res=300)
# leg <- get_legend(res_fig0)
# res_fig0 <- res_fig0 + theme(legend.position = "none")
# res_fig1 <- res_fig1 + theme(legend.position = "none")
# res_fig2 <- res_fig2 + theme(legend.position = "none")
# res_fig3 <- res_fig3 + theme(legend.position = "none")
# res_fig4 <- res_fig4 + theme(legend.position = "none")
ggarrange(res0_fig_tab, res1_fig_tab, res2_fig_tab, res3_fig_tab, res4_fig_tab, leg, nrow=2, ncol=3)
#dev.off()
```

```{r fig.width=9, fig.height=6}
#tiff("res_sim2_exp_s.tiff", units="in", width=9, height=6, res=300)
#jpeg("res_sim2_exp_s.jpeg", units="in", width=9, height=6, res=300)
res_fig(result0, result1, result2, result3, result4)
#dev.off()
```

```{r fig.width=7, fig.height=4, warning=FALSE, message=FALSE, eval=FALSE}
# Bias graph
betas <- rep(c(log(1), log(1.10), log(1.15), log(1.25), log(1.5), log(2)), 5)
bias <- c(result0[, "Bias"], result1[, "Bias"], result2[, "Bias"], result3[, "Bias"], result4[, "Bias"])
sd_bias <- c(result0[, "SD"], result1[, "SD"], result2[, "SD"], result3[, "SD"], result4[, "SD"])
error <- factor(c(rep("None", 6), rep("Independent", 6), rep("Exposure", 6), rep("Confounder", 6), rep("Covariate", 6)), levels=c("None", "Independent", "Exposure", "Confounder", "Covariate"))
lb <- bias - qnorm(0.975)*sd_bias/sqrt(5000)
ub <- bias + qnorm(0.975)*sd_bias/sqrt(5000)
bias_df <- data.frame(betas, bias, error, lb, ub)

bias_tab_df <- data.frame(rbind(t(round(bias[1:6],4)), t(round(bias[7:12],4)), t(round(bias[13:18],4)), t(round(bias[19:24],4)), t(round(bias[25:30],4))))
rownames(bias_tab_df) <- c("None", "Independent", "Exposure", "Confounder", "Covariate")
colnames(bias_tab_df) <- c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)")
bias_tab <- tableGrob(bias_tab_df, theme = ttheme_minimal(core=list(fg_params=list(col=c("#E76BF3", "#00B0F6","#00BF7D", "#F8766D", "#A3A500"))), rowhead=list(fg_params=list(fontface="plain")), base_size=10))

bias_fig <- ggplot(bias_df, aes(x=betas, y=bias, col=error)) + geom_point(position=position_dodge(0.04)) + geom_errorbar(aes(ymin=lb, ymax=ub, width=0.03), position=position_dodge(0.04)) + geom_hline(yintercept=0, linetype="dashed", color="black") + labs(x="Beta Coefficient for Exposure, z", y="Bias", title="Bias of Beta Coefficient for Exposure, z, from Model 1 (Cox)", color="Error") + theme_bw() + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_text(angle=30, vjust=0.72)) + scale_x_continuous(breaks=c(log(1), log(1.1), log(1.15), log(1.25), log(1.5), log(2)), labels=c("log(1)", "log(1.1)", "log(1.15)", "log(1.25)", "log(1.5)", "log(2)"))

bias_fig_nl <- bias_fig + theme(legend.position = "none")
bias_fig_tab <- ggarrange(bias_fig_nl, bias_tab, nrow=2, heights=c(2,1)) 

#jpeg("bias_sim2_exp_s.jpeg", units="in", width=7, height=4, res=300)
bias_fig
#dev.off()
```

```{r}
result0_exp_s_sim2 <- result0
result1_exp_s_sim2 <- result1
result2_exp_s_sim2 <- result2
result3_exp_s_sim2 <- result3
result4_exp_s_sim2 <- result4
```

